### 2015-05-18 manuscript20150320/plos_template.tex
backup manuscript as of 20150320

Finally, we have applied the proposed method for the somatic mutation data of 30 cancer types \cite{pmid23945592}.
The proposed method was applied on each cancer type separately to see the robustness of the estimated signatures across different cancer types.
By changing the number of mutation signatures and examining values of the log-likelihood and bootstrap errors as well as correlation of membership parameters,
we have chosen the number of mutation signatures for each cancer type.
Finally, similar mutation signatures observed across cancer types were clustered by Frobenius Distance.
 % (see Supplementary Material for the values of the log-likelihoods and bootstrap errors for each cancer type).

>>>>

Finally, we have applied the proposed method for the somatic mutation data of 30 cancer types \cite{pmid23945592}.
The proposed method was applied on each cancer type separately to see the robustness of the estimated signatures across different cancer types.
By changing the number of mutation signatures and examining values of the log-likelihood and bootstrap errors as well as correlation of membership parameters,
we have chosen the number of mutation signatures for each cancer type
(see Supplementary Table 1 for the number of mutation signatures chosen for each cancer type).
Finally, similar mutation signatures observed across cancer types were clustered by Frobenius Distance.
 % (see Supplementary Material for the values of the log-likelihoods and bootstrap errors for each cancer type).
